---
title: "rstudio::conf 2020"
author: "Josh Johnston"
date: "2/2/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Things I Learned @ rconf 


San Francisco has a homeless problem.  Feb 3rd 12:36 udpate.

I attended the applied machine learning workshop.  Course material for all workshops is available here: 
<https://github.com/rstudio-conf-2020>.

There were four different tracks running simultaneously during the conference.  Unfortunately, the material wasn't aggregated from each track.  I'll share some highlights from the sessions that I attended.  



## Package Development

Everyone should create a package in R.  Rmarkdown, Git, and Roxygen2 make creating a package fairly easy.  

I created a package that quickly creates a control chart for process monitoring.  

## Shiny App

Everyone should create a Shiny app.  I created a Shiny app to evaluate complaint groupings.


## Rmarkdown 

Marianne attending the Rmarkdown workshop, so I'll let her elaborate, but Rmarkdown can do some amazing things.  I created this slide deck in Rmarkdown.  

## Git / Github

Github is a great tool for implementing version control on your projects.  It also makes sharing, collaborating, and hosting solutions very easy.  You should all create a free github account and get familiar with the Rstudio / github integration features.  


## Predictive Modeling

Models are generally categorized as regression or classification.  

- Use R for predictive modeling

- List types of Regression models
-- Linear Regression

- Classification Models
-- Random Forrests
-- Boosted Trees

- Hybrid Models
-- MARS
-- SVM


## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

